\documentclass{tufte-handout}
\usepackage{microtype}
\usepackage{booktabs}

\begin{document}
\section{Disjoint Sets I, Report}

by Alice Cooper\sidenote{Complete the report by filling
  in your real name, filling in the parts marked $[\ldots]$ and changing other parts wherever necessary.
  (For instance, the numbers is the tables are nonsense right now.)
  Remove the sidenotes in your final hand-in.}

  \subsection{Results}
  
  I solved this exercise in Python 3 / Java.

  Program \texttt{ds1} uses Java's \texttt{HashSet} and fails on tests $[\cdots]$ with error $[\cdots]$ / passes all the instances on CodeJudge.%
  \sidenote{Replace by whichever library class you actually use, and whichever errors you generated.}

  The following table gives a rough estimate on the running time for larger instances, based on experiments and extrapolating observed behaviour for smaller instances on my machine.\sidenote{
    The numbers in the example table are completely made up and have to be replaced.
  If you \emph{want} to be more precise, you may.
  If you \emph{want} to give averages and standard deviations  for your experiments (because you've learned that) yo may.
  If you \emph{want} to present the data graphically instead of a table, you may.
  If you \emph{want} to present the data for different $n$ and $m$, you may.
}

\bigskip
  \begin{tabular}{lll}
  \toprule
    Size          & Time for \texttt{ds1}   \\\midrule
    $n, m = 10^5$ & 13.5 s \\
    $n, m = 10^6$ & 3h 20m  \\
    $n, m = 10^7$ & ca 1 week (extrapolated) \\
    $n, m = 10^8$ & ca 1 day (extrapolated)  \\
    $n, m = 10^9$ & ca 1 day (extrapolated) \\
  \bottomrule
  \end{tabular}
\end{document}

